Synthesising Complex Termination Arguments

### 2014-06-02 papers/termination/paper.tex
Reword conjectures

\begin{theorem}
 \textsc{Headshot} is biased towards finding ranking functions with low
 Kolmogorov complexity.
\end{theorem}

\begin{conjecture}
 Most low-Kolmogorov-complexity programs compute non-linear functions.
\end{conjecture}

@@

\begin{conjecture}
 Low-Kolmogorov-complexity (LKC) programs have LKC ranking functions.
\end{conjecture}

>>>>

\begin{theorem}
 \textsc{Headshot} is biased towards finding ranking functions with
 low-Kolmogorov-complexity (LKC).
\end{theorem}

\begin{conjecture}
 Most LKC programs compute non-linear functions, but linear functions are LKC.
 So LKC is a weaker assumption than linearity.
\end{conjecture}

@@

\begin{conjecture}
 LKC programs have LKC ranking functions (almost certainly false).
\end{conjecture}
